### 2022-04-08 manuscript.tex
Update 04.singlecell.md [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/2f23247bfc2eab5c45c9690621aa3a1e3a7242e9.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/2f23247bfc2eab5c45c9690621aa3a1e3a7242e9/checks
https://github.com/scherzerthesis/thesis/actions/runs/2116018342

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/bd0e4c0d29a553d0a2e15f89b42a89cd700418db/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/bd0e4c0d29a553d0a2e15f89b42a89cd700418db}{scherzerthesis/thesis@bd0e4c0}
on April 8, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_4.png}
\caption{\textbf{Figure 4.5. MAPK pathway transcriptional sigure is identifed in BRAV\textsuperscript{V600E} tumor models.} (A) Heatmap of top differentially expressed genes. (B) Program score of MAPK pathway activation}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_5.png}
\caption{\textbf{Figure 4.6. P53 transcriptional signature is identified in BRAV\textsuperscript{V600E}, p53-wildtype tumor cells.} (A) Heatmap of top differentially expressed genes in p53 pathway. (B) P53 program score is revealed to be upregulated in only p53-wildtype mice.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_6.png}
\caption{\textbf{Figure 4.7. Heatmap of top Genotpye-specific gene expression changes.}}\label{fig:04}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/2f23247bfc2eab5c45c9690621aa3a1e3a7242e9/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/2f23247bfc2eab5c45c9690621aa3a1e3a7242e9}{scherzerthesis/thesis@2f23247}
on April 8, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_5.png}
\caption{\textbf{Figure 4.5. MAPK pathway transcriptional sigure is identifed in BRAV\textsuperscript{V600E} tumor models.} (A) Heatmap of top differentially expressed genes. (B) Program score of MAPK pathway activation}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_6.png}
\caption{\textbf{Figure 4.6. P53 transcriptional signature is identified in BRAV\textsuperscript{V600E}, p53-wildtype tumor cells.} (A) Heatmap of top differentially expressed genes in p53 pathway. (B) P53 program score is revealed to be upregulated in only p53-wildtype mice.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_7.png}
\caption{\textbf{Figure 4.7. Heatmap of top Genotpye-specific gene expression changes.}}\label{fig:04}
}
\end{figure}
